flowers-pilot-analysis

### 2021-08-24 code/aa-flowers-pilot_analysis.Rmd
update code bits

```{r}
d.by_player_metrics %>% group_by(gameId, condition, languageCondition, playerId) %>% 
  summarize(mean_player_utility = mean(playerUtility)) %>%
  group_by(condition, languageCondition) %>% 
  summarize_at("mean_player_utility", funs(mean, min, max, sd))
```
## Simple Distributions
### Points

>>>>

What is the spread of participant earnings over entire games, is there a diff here?

```{r}
d.by_player_metrics %>% group_by(gameId, condition, languageCondition, playerId) %>% 
  summarize(mean_player_utility = mean(playerUtility)) %>%
  group_by(condition, languageCondition) %>% 
  summarize_at("mean_player_utility", funs(mean, min, max, sd))
```
What is the spread of participant earnings in ind. trials (average earning per participant per trial)
```{r}
d.by_player_metrics %>% group_by(condition, languageCondition) %>% 
  summarize_at("playerUtility", funs(mean, min, max, sd))
```

## Simple Distributions
### Points
